shipboard-flask

### 2024-08-26 examples/shipboard-flask.Rmd
shipboard flask

---
title: "surface-flask"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{surface-flask}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

```{r readnc, eval = T}
datasetid <- "surface-flask"
df <- obs_read_nc(index = index,
                  categories = datasetid,
                  solar_time = TRUE,
                  verbose = TRUE)

@@

```{r spatial, eval = T}
north <- 80
south <- 10
west <- -170
east <- -50
max_altitude <- 8000
yy <- 2020
evening <- 14

@@

df <- df[altitude_final < max_altitude &
           latitude < north &
           latitude > south &
           longitude < east &
           longitude > west]
dim(df)
```

@@

```{r}
df3 <- df2[hour_st %in% evening]
df3[, c("solar_time", "solar_time_cut")]

@@

```{r csvy, eval = T}
cat("\nAdding notes in csvy:\n")
notes <- c(paste0("sector: ", datasetid),
           paste0("timespan: ", yy),
           paste0("spatial_limits: north = ", north, ", south = ", south, ", east = ", east, ", west = ", west),
           "data: Data averaged every 20 seconds",
           paste0("altitude: < ", max_altitude),
           paste0("hours: ", evening),
           "local_time: used solar_time")

@@

```{r obs_plotsave, fig.width=5, fig.height=3, eval = T, echo = F, message=F, warning=F}
png("../man/figures/obsplot_surfaceflask.png", width = 1500, height = 1000, res = 200)
obs_plot(df3, time = "timeUTC", yfactor = 1e9)
dev.off()
```

@@

![](https://github.com/noaa-gml/rtorf/blob/main/man/figures/obsplot_surfacetflask.png?raw=true)

```{r savesf, fig.width=5, fig.height=3, eval = T, echo = F}
library(sf)
dx <- df4[, 
    lapply(.SD, mean),
    .SDcols = "value",
    by = .(latitude, longitude)]
x <- st_as_sf(dx, coords = c("longitude", "latitude"), crs = 4326)
png("../man/figures/obsplot_surfaceflask_map.png", width = 1500, height = 1000, res = 200)
plot(x["value"], axes = T, reset = F)
maps::map(add = T)
dev.off()
```

@@

![](https://github.com/noaa-gml/rtorf/blob/main/man/figures/obsplot_surfaceflask_map.png?raw=true)

>>>>

---
title: "shipboard-flask"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{shipboard-flask}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

@@

```{r readnc, eval = T}
datasetid <- "shipboard-flask"
df <- obs_read_nc(index = index,
                  categories = datasetid,
                  solar_time = TRUE,
                  verbose = TRUE)

@@

```{r spatial, eval = T}
yy <- 2020
evening <- 14

@@

dim(df)
```

@@

```{r}
df3 <- df2
df3[, c("solar_time", "solar_time_cut")]
```

@@

```{r csvy, eval = T}
cat("\nAdding notes in csvy:\n")
notes <- c(paste0("sector: ", datasetid),
           paste0("timespan: ", yy),
           paste0("hours: ", evening),
           "local_time: used solar_time")

@@

```{r obs_plotsave, fig.width=5, fig.height=3, eval = T, echo = F, message=F, warning=F}
png("../man/figures/obsplot_shipboardflask.png", width = 1500, height = 1000, res = 200)
obs_plot(df3, time = "timeUTC", yfactor = 1e9)
dev.off()
```

@@

![](https://github.com/noaa-gml/rtorf/blob/main/man/figures/obsplot_shipboardflask.png?raw=true)

```{r savesf, fig.width=5, fig.height=3, eval = T, echo = F}
library(sf)
dx <- df4[, 
    lapply(.SD, mean),
    .SDcols = "value",
    by = .(latitude, longitude)]
x <- st_as_sf(dx, coords = c("longitude", "latitude"), crs = 4326)
png("../man/figures/obsplot_shipboardflask_map.png", width = 1500, height = 1000, res = 200)
plot(x["value"], axes = T, reset = F)
maps::map(add = T)
dev.off()
```

@@

![](https://github.com/noaa-gml/rtorf/blob/main/man/figures/obsplot_shipboardflask_map.png?raw=true)
